DeepSphere: a graph-based spherical CNN

### 2019-09-25 main.tex
Updates from Overleaf

\usepackage{hyperref}
\usepackage{url}
\usepackage{breqn}
\usepackage{booktabs}
\usepackage{siunitx} % used in SHREC table
\usepackage{bbm}        % for mathbbm
\usepackage{graphicx} \graphicspath{{figures/}}
\usepackage[export]{adjustbox} % figure vertical alignment
\usepackage{subfig}
%\usepackage{wrapfig}
%\usepackage{floatflt}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}

@@

\todo{
\begin{itemize}
	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN.
	\item adjacency matrix: $A$ instead of $W$?
	\item anonymize DeepSphere citation
% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
	\item citet for inline, citep for parenthesis
	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method.
	\item PSD of climate data: how does it compare to cosmo and 3D objects?
	\item align the spheres in figure 1
	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
	\item check footnotes
	\item climate data on spectrum plot
	\item result tables: only what supports the main message in the text, everything we have in the appendix
	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions. Irregular, uneven. Coarsening, down-sampling.
	\item check English vs American English
	\item unify enumerations. I like (i), (ii), etc.
	\item notation: should we use indices from 1 to n instead of 0 to n-1 for compactness?
	\item add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere.
	\item figure placements
	\item do the experiments on the icosahedral grid with the pooling as defined in the paper
	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
	\item update pygsp and merge sphere branch
	\item check that NN architectures and hyper-params are correctly reported
	\item keep NN architecture and hyper-params in the main text? Move the paragraph to appendix if not enough space.
	\item shall we still site adam and batch norm?
	\item check results on ModelNet40
\end{itemize}
}
\newpage

@@

\section{Method [1 pages]}

@@

\section{Graph convolution and equivariance [2 pages]} \label{sec:equivariance}
%\section{Is graph convolution equivariant to rotation? [2 pages]} \label{sec:equivariance}

@@

We require $F_\V$ to be a suitable subspace of $L^2(\S^2)$ such that $T_\V$ is invertible, i.e., the function $f \in F_\V$ can be unambiguously reconstructed from its sampled values $\b{f}$.
The existence of such a subspace depends on the sampling scheme $\V$, and its characterization is a common problem in signal processing \citep{driscoll1994Fouriersphere}.
For most sampling schemes, it is not known if $F_\V$ exists and hence if $T_\V$ is invertible.
A special case is the equiangular sampling scheme where a sampling theorem holds, and thus a closed form of $T_\V^{-1}$ is known. % \cite{driscoll1994Fouriersphere}
For sampling schemes where no such sampling formula is available, we leverage the discrete SHT to reconstruct $f$ from $\b{f}$, thus approximating $T_\V^{-1}$.
For all theoretical considerations, we assume that $F_\V$ exists and $f \in F_\V$.

% 0.2 Explain why the Laplacian is so important...
By definition, our (spherical) graph convolution is rotation equivariant, if and only if, it commutes with the rotation operator defined as $R(g), g\in SO(3)$: $R(g) f(x) = f\left(g^{-1} x \right)$.
In the context of this work, graph convolution is performed by recursive applications of the graph Laplacian (\eqnref{graph_conv}).
Hence, if $\b{L}$ commutes with the rotation operator, then, by recursion, it will also commute with the convolution $h(\b{L})$.
As a result, to simplify our analysis, we concentrate on the graph Laplacian and $h(\b{L})$ is rotational invariant if and only if
% 0.3 Formulate the problem
\mart{Correct formula for equivariance error and the corresponding plots as soon as you changed it!}
\begin{equation} \label{eq:equivariance}
	\b{R}_\V(g) \b{L} \b{f} = \b{L} \b{R}_\V(g) \b{f} \hspace{1cm} \forall f\in F_\V \text{ and } \forall g\in SO(3),
\end{equation}
where $\b{R}_\V(g) = T_\V R(g) T_\V^{-1}$. For practical a evaluation of the equivariance, we define the \textit{normalized equivariance error} for a signal $\b{f}$, and a  rotation $g$ as:
\begin{equation} \label{eq:equivariance error}
	E_{\b{L}}(\b{f}, g) = \left(\frac{ \norm {\b{R}_\V(g) \b{L} \b{f} - \b{L} \b{R}_\V(g) \b{f}} }{\norm {\b{L} \b{f}}}\right)^2,
\end{equation}
More generally for a class of signal $f \in C \subset F_\V$, the \textit{mean equivariance error}
\begin{equation} \label{eq:mean equivariance error}
	\overline E_{\b{L}, C} = \mathbb E_{\b{f}\in C, g\in SO(3)} \ E_{\b{L}}(\b{f}, g).
\end{equation}
\mart{Talk about the probability measure used on C, SO(3)?}
In practice, to analyze the equivariance error frequency,  the set $C$ we used is composed of functions $f$ made of spherical harmonic of a single degree $\ell$.
The expected value is obtained by averaging over a finite number of random functions and random rotations.

\subsection{Finding the optimal set of weights}  \label{sec:optimal}

% 1) summary the work of Khasanova
\cite{khasanova2017sphericalcnn} designed a Laplacian $\b{L}$ explicitly intended to work with the equiangular sampling.
They consider the set $\mathcal{G}$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude latitude axis.
Their approach leads to weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
\begin{equation} \label{eqn:weights:khasanova}
	w_{ij} = \frac{1}{\norm{x_i-x_j}}
\end{equation}

\begin{figure}
	\centering
	\includegraphics[width=0.4\linewidth]{kernel_widths}
	\caption{
		Optimal kernel widths for various resolutions of the HEALPix grid.
	}
	\label{fig:kernel_widths}
\end{figure}

% 2) explain our approach
We chose a different approach and take inspiration from \cite{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta_{\mathbb{S}^2}$ as the number of sampling points goes to infinity.
This convergence result is important as a) $\Delta_{\mathbb{S}^2}$ commutes with rotation ($\Delta_{\mathbb{S}^2}R(g) = R(g)\Delta_{\mathbb{S}^2}$) and b) is diagonalized by the spherical harmonics.
In this case the weighting scheme is full (every node is connected to every node) and is based on the exponential kernel:
\begin{equation} \label{eqn:weights:belkin}
w_{ij} = e^{-\frac{1}{4t} \norm{x_i-x_j}^2}
\end{equation}
In practice most of the weights are very close to $0$ and hence, to optimize for computational efficiency, we limit ourselves to only the $k$ nearest neighbors.
Given $k$, the optimal $t$ is found by searching for the minimizer of \eqref{eq:mean equivariance error}.
\Figref{kernel_widths} shows the optimal kernel widths found for various resolutions of the HEALPix grid.

@@

% 3.1) explain what the figures tell us
From 20\% error on V1, we got to less than 2\% error on V2. The number of neighbors used for V2 is $50$. More neighbors implies naturally more precision, plus a better kernel width obtained by "minimizing" the equivariance error. \mart{How to explain how we found the kernel width? Micha\"el I need your help here!!} Literally, minimizing the kernel width would lead to a completely disconnected graph. What we did was finding a heuristic law (fix neighbors, set the kernel width $\hat t$ by imposing the minimum weight to be equal to $0.1$) and then minimizing the equivariance error in the range $(\hat t / 10, \hat t\cdot 10) $. We got better that Khasanova-Frossard \mart{(check the code)} that however uses only 4 neighbors. However, it is built to explicitely minimize the equivariance error, so we expect it to be a good benchmark against which to test our construction.
\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{DeepSphereV1}
	\caption{Shall we put it here or in Appendix?
	}
	\label{fig:deepsphereV1}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{DeepSphereV2_50neighbors.pdf}
	\caption{}
	\label{fig:deepsphereV2}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{khasanova_frossard.pdf}
	\caption{}
	\label{fig:khasanova_frossard}
\end{figure}

@@

\begin{table}
    \centering
    \begin{tabular}{l c c c}
		\toprule
		& accuracy & conv. equiv. error & NN inv. error \\
		\midrule
		2D CNN baseline \citep{perraudin2019deepspherecosmo} & \todo{??} & \todo{can we?} \\
		8 neighbors, $\hat{t} = ??$, CNN variant, \citep{perraudin2019deepspherecosmo} & \todo{??} & \todo{??} \\
		8 neighbors, $\hat{t} = ??$, FCN variant, \citep{perraudin2019deepspherecosmo} & \todo{??} & \todo{??} \\
		8 neighbors, optimal kernel width $\hat{t} = ??$ & \todo{??} & \todo{??} \\
		20 neighbors, optimal kernel width $\hat{t} = ??$ & \todo{??} & \todo{??} \\
		40 neighbors, optimal kernel width $\hat{t} = ??$ & \todo{??} & \todo{??} \\
		\bottomrule
    \end{tabular}
	\caption{
		Results on the classification of partial convergence maps.
		\todo{While extreme non-equivariance (the 2D CNN baseline) penalizes performance, improving equivariance doesn't improve performance.}
	}
    \label{tab:cosmo}
\end{table}

@@

\paragraph{Preliminaries.}
The proof of theorem \ref{theo:pointwise convergence for a regular sampling} is inspired from the work of \cite{belkin2005towards}. As a result, we start by restating some of their results.
Given a sampling $V = \{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a closed, compact and infinitely differentiable manifold $\mathcal{M}$, a smooth ($\in\mathcal{C}_\infty(\mathcal{M)}$) function  $f:\mathcal{M} \rightarrow \mathbb{R}$, and defined the vector $\b{f}$ of samples of $f$ as follows: $T_\V f = \b{f} \in \mathbb{R}^n,\ \b{f}_i = f(x_i)$.
The proof is constructed by leveraging 3 different operators:
\begin{itemize}
    \item The extended graph Laplacian operator is a functional $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$  is defined given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ and $y\in \mathcal{M}$  as
	\begin{equation}
	\label{eq:Heat Kernel Graph Laplacian operator}
	 L_n^tf(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
	\end{equation}
	Note that we have the following relation $\b{L}_n^t \b{f} = T_\V L_n^t f$.
	\item The functional approximation to the Laplace-Beltrami operator is a functional $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ defined  as
	\begin{equation}
    \label{eq:Functional approximation to the Laplace-Beltrami operator}
	L^tf(y) = \int_{\mathcal{M}} \exp^{-\frac{\|y-x\|^2}{4t}}\left(f(y)-f(x)\right)d\mu(x),
	\end{equation}
	where given $\mu$ be the uniform probability measure on the manifold $\mathcal{M}$, and let $\text{vol}(\mathcal{M})$ be the volume of $\mathcal{M}$.
	\item
	The Laplace-Beltrami operator $\Delta_{\mathcal{M}}$ is defined as the divergence of the gradient
	\begin{equation}
        \label{eq:laplace-beltrami}
        \Delta_{\mathcal M}f(y):= -\text{div}(\nabla_{\mathcal M}f)
    \end{equation}
    of a differentiable function $f: \mathcal M\rightarrow \R$. The gradient $\nabla f: \mathcal M \rightarrow T_p\mathcal M$ is a vector field defined on the manifold pointing towards the direction of steepest ascent of $f$, where $T_p\mathcal M$ is the affine space of all vectors tangent to $\mathcal M$ at $p$

@@

Leaveraging these three operators \cite{belkin2005towards, belkin2007convergence} have build proofs of both pointwise and spectral convergence of the extended graph Laplacian toward the Laplace-Beltrami operator.
The proofs consists in establishing that \eqref{eq:Heat Kernel Graph Laplacian operator} converges toward \eqref{eq:Functional approximation to the Laplace-Beltrami operator} as $n\rightarrow \infty$ and \eqref{eq:Functional approximation to the Laplace-Beltrami operator} converges toward \eqref{eq:laplace-beltrami} as $t\rightarrow 0$. In particular, this second step is given by the following:
\begin{prop}
[\cite{belkin2005towards}, Proposition 4.4]
Let $\mathcal{M}$ be a $k$-dimensional compact smooth manifold embedded in some Euclidean space $\mathbb{R}^N$, and fix $y\in\mathcal{M}$. Let $f\in\mathcal{C}_\infty(\mathcal{M)}$. Then
\begin{equation}
\frac{1}{t}\frac{1}{(4\pi t)^{k/2}} L^tf(y) \xrightarrow{t\to 0 } \frac{1}{\text{vol}(\mathcal M)}\Delta_{\mathcal M}f(y).
\end{equation}
\label{prop:3}
\end{prop}

>>>>

\usepackage{hyperref}
\usepackage{url}
\usepackage{breqn}
\usepackage{booktabs}
\usepackage{siunitx} % used in SHREC table
\usepackage{bbm}        % for mathbbm
\usepackage{graphicx} \graphicspath{{figures/}}
\usepackage[export]{adjustbox} % figure vertical alignment
\usepackage{subfig}
%\usepackage{wrapfig}
%\usepackage{floatflt}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{wrapfig}

@@

\todo{
\begin{itemize}
	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN.
	\item adjacency matrix: $A$ instead of $W$?
	\item anonymize DeepSphere citation
% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
	\item citet for inline, citep for parenthesis
	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method.
	\item PSD of climate data: how does it compare to cosmo and 3D objects?
	\item align the spheres in figure 1
	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
	\item check footnotes
	\item climate data on spectrum plot
	\item result tables: only what supports the main message in the text, everything we have in the appendix
	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions. Irregular, uneven. Coarsening, down-sampling.
	\item check English vs American English
	\item unify enumerations. I like (i), (ii), etc.
	\item notation: should we use indices from 1 to n instead of 0 to n-1 for compactness?
	\item add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere.
	\item figure placements
	\item do the experiments on the icosahedral grid with the pooling as defined in the paper
	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
	\item update pygsp and merge sphere branch
	\item check that NN architectures and hyper-params are correctly reported
	\item keep NN architecture and hyper-params in the main text? Move the paragraph to appendix if not enough space.
	\item shall we still site adam and batch norm?
	\item check results on ModelNet40
	\item Check that HEALPix is introduced in the introduction
\end{itemize}
}
\newpage

@@

\section{Method}

@@

\section{Graph convolution and equivariance} \label{sec:equivariance}
%\section{Is graph convolution equivariant to rotation? [2 pages]} \label{sec:equivariance}

@@

We require $F_\V$ to be a suitable subspace of $L^2(\S^2)$ such that $T_\V$ is invertible, i.e., the function $f \in F_\V$ can be unambiguously reconstructed from its sampled values $\b{f}$.
The existence of such a subspace depends on the sampling scheme $\V$, and its characterization is a common problem in signal processing \citep{driscoll1994Fouriersphere}.
For most sampling schemes, it is not known if $F_\V$ exists and hence if $T_\V$ is invertible.
A special case is the equiangular sampling scheme where a sampling theorem holds, and thus a closed form of $T_\V^{-1}$ is known. % \cite{driscoll1994Fouriersphere}
For sampling schemes where no such sampling formula is available, we leverage the discrete SHT to reconstruct $f$ from $\b{f}=T_\V f$, thus approximating $T_\V^{-1}$.
For all theoretical considerations, we assume that $F_\V$ exists and $f \in F_\V$.

% 0.2 Explain why the Laplacian is so important...
By definition, the (spherical) graph convolution is rotation equivariant, if and only if, it commutes with the rotation operator defined as $R(g), g\in SO(3)$: $R(g) f(x) = f\left(g^{-1} x \right)$.
In the context of this work, graph convolution is performed by recursive applications of the graph Laplacian (\eqnref{graph_conv}).
Hence, if $\b{L}$ commutes with the rotation operator, then, by recursion, it will also commute with the convolution $h(\b{L})$.
As a result, to simplify our analysis, we concentrate on the graph Laplacian and $h(\b{L})$ is rotational invariant if and only if
% 0.3 Formulate the problem
\begin{equation} \label{eq:equivariance}
	\b{R}_\V(g) \b{L} \b{f} = \b{L} \b{R}_\V(g) \b{f} \hspace{1cm} \forall f\in F_\V \text{ and } \forall g\in SO(3),
\end{equation}
where $\b{R}_\V(g) = T_\V R(g) T_\V^{-1}$. For practical a evaluation of the equivariance, we define the \textit{normalized equivariance error} for a signal $\b{f}$, and a  rotation $g$ as:
\begin{equation} \label{eq:equivariance error}
	E_{\b{L}}(\b{f}, g) = \left(\frac{ \norm {\b{R}_\V(g) \b{L} \b{f} - \b{L} \b{R}_\V(g) \b{f}} }{\norm {\b{L} \b{f}}}\right)^2,
\end{equation}
More generally for a class of signal $f \in C \subset F_\V$, the \textit{mean equivariance error} defined as
\begin{equation} \label{eq:mean equivariance error}
	\overline E_{\b{L}, C} = \mathbb E_{\b{f}\in C, g\in SO(3)} \ E_{\b{L}}(\b{f}, g),
\end{equation}
represents well the overall equivariance error.
In practice, we analyse this error with respect of the frequency by setting the set $C$ to functions $f$ made of single degree spherical harmonic.
The expected value is obtained by averaging over a finite number of random functions and random rotations.

\subsection{Finding the optimal set of weights}  \label{sec:optimal}
% 1) summary the work of Khasanova
Naturally, \cite{khasanova2017sphericalcnn} designed a Laplacian $\b{L}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude and latitude axis. 
Working specifically with the equiangular sampling, they consider the set $\mathcal{G}$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East).
% and propose a weighting scheme $w_{ij}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude latitude axis.
Their approach leads to weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
\begin{equation} \label{eqn:weights:khasanova}
	w_{ij} = \frac{1}{\norm{x_i-x_j}}
\end{equation}

\begin{wrapfigure}{r}{5.5cm}
	\centering
	\vspace{-0.3cm}
	\includegraphics[width=5cm]{kernel_widths}
	\caption{
		Optimal kernel widths for various resolutions of the HEALPix grid and numbers of neighbors.
	}
	\label{fig:kernel_widths}
\end{wrapfigure}
% 2) explain our approach
We chose a different approach and take inspiration from \cite{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta_{\mathbb{S}^2}$ as the number of sampling points goes to infinity.
This convergence result is important as a) $\Delta_{\mathbb{S}^2}$ commutes with rotation ($\Delta_{\mathbb{S}^2}R(g) = R(g)\Delta_{\mathbb{S}^2}$) and b) is diagonalized by the spherical harmonics.
In this case the weighting scheme is full (every node is connected to every node) and is based on the exponential kernel:
\begin{equation} \label{eqn:weights:belkin}
w_{ij} = e^{-\frac{1}{4t} \norm{x_i-x_j}^2}
\end{equation}
In practice, because of the exponential, most of the weights are very close to $0$. Hence, to optimize for computational efficiency, we limit ourselves to only the $k$ nearest neighbors.
Given $k$, the optimal $t$ is found by searching for the minimizer of \eqref{eq:mean equivariance error}.
\Figref{kernel_widths} shows the optimal kernel widths found for various resolutions of the HEALPix grid.

@@

% 3.1) explain what the figures tell us
From 20\% error on V1, we got to less than 2\% error on V2. The number of neighbors used for V2 is $50$. More neighbors implies naturally more precision, plus a better kernel width obtained by "minimizing" the equivariance error. \mart{How to explain how we found the kernel width? Micha\"el I need your help here!!} Literally, minimizing the kernel width would lead to a completely disconnected graph. What we did was finding a heuristic law (fix neighbors, set the kernel width $\hat t$ by imposing the minimum weight to be equal to $0.1$) and then minimizing the equivariance error in the range $(\hat t / 10, \hat t\cdot 10) $. We got better that Khasanova-Frossard \mart{(check the code)} that however uses only 4 neighbors. However, it is built to explicitely minimize the equivariance error, so we expect it to be a good benchmark against which to test our construction.
\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{V1.pdf}
	\caption{V1}
	\label{fig:deepsphereV1}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{V2.pdf}
	\caption{V2, 20 neighbors}
	\label{fig:deepsphereV2}
\end{figure}

@@

\begin{table}
    \centering
    \begin{tabular}{l c c c}
		\toprule
		& accuracy & conv. equiv. error & NN inv. error \\
		\midrule
		2D CNN baseline \citep{perraudin2019deepspherecosmo} & \todo{??} & \todo{can we?} \\
		8 neighbors, $\hat{t} = ??$, CNN variant, \citep{perraudin2019deepspherecosmo} & \todo{??} & \todo{??} \\
		8 neighbors, $\hat{t} = ??$, FCN variant, \citep{perraudin2019deepspherecosmo} & 83.8 & \todo{??} \\
		8 neighbors, optimal kernel width $\hat{t} = ??$ & 87.1 & \todo{??} \\
		20 neighbors, optimal kernel width $\hat{t} = ??$ & 91.25 & \todo{??} \\
		40 neighbors, optimal kernel width $\hat{t} = ??$ & \todo{??} & \todo{??} \\
		\bottomrule
    \end{tabular}
	\caption{
		Results on the classification of partial convergence maps.
		\todo{While extreme non-equivariance (the 2D CNN baseline) penalizes performance, improving equivariance doesn't improve performance.}
	}
    \label{tab:cosmo}
\end{table}

@@

\paragraph{Preliminaries.}
The proof of theorem \ref{theo:pointwise convergence for a regular sampling} is inspired from the work of \cite{belkin2005towards}. As a result, we start by restating some of their results.
Given a sampling $V = \{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a closed, compact and infinitely differentiable manifold $\mathcal{M}$, a smooth ($\in\mathcal{C}_\infty(\mathcal{M)}$) function  $f:\mathcal{M} \rightarrow \mathbb{R}$, and defined the vector $\b{f}$ of samples of $f$ as follows: $T_\V f = \b{f} \in \mathbb{R}^n,\ \b{f}_i = f(x_i)$.
The proof is constructed by leveraging 3 different operators:
\begin{itemize}
    \item The extended graph Laplacian operator is a linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$  is defined given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ and $y\in \mathcal{M}$  as
	\begin{equation}
	\label{eq:Heat Kernel Graph Laplacian operator}
	 L_n^tf(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
	\end{equation}
	Note that we have the following relation $\b{L}_n^t \b{f} = T_\V L_n^t f$.
	\item The functional approximation to the Laplace-Beltrami operator is a linear operator $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ defined  as
	\begin{equation}
    \label{eq:Functional approximation to the Laplace-Beltrami operator}
	L^tf(y) = \int_{\mathcal{M}} e^{-\frac{\|x-y\|^2}{4t}}\left(f(y)-f(x)\right)d\mu(x),
	\end{equation}
	where given $\mu$ be the uniform probability measure on the manifold $\mathcal{M}$, and let $\text{vol}(\mathcal{M})$ be the volume of $\mathcal{M}$.
	\item
	The Laplace-Beltrami operator $\Delta_{\mathcal{M}}$ is defined as the divergence of the gradient
	\begin{equation}
        \label{eq:laplace-beltrami}
        \Delta_{\mathcal M}f(y):= -\text{div}(\nabla_{\mathcal M}f)
    \end{equation}
    of a differentiable function $f: \mathcal M\rightarrow \R$. The gradient $\nabla f: \mathcal M \rightarrow T_p\mathcal M$ is a vector field defined on the manifold pointing towards the direction of steepest ascent of $f$, where $T_p\mathcal M$ is the affine space of all vectors tangent to $\mathcal M$ at $p$.

@@

Leveraging these three operators \cite{belkin2005towards, belkin2007convergence} have build proofs of both pointwise and spectral convergence of the extended graph Laplacian toward the Laplace-Beltrami operator.
The proofs consists in establishing that \eqref{eq:Heat Kernel Graph Laplacian operator} converges toward \eqref{eq:Functional approximation to the Laplace-Beltrami operator} as $n\rightarrow \infty$ and \eqref{eq:Functional approximation to the Laplace-Beltrami operator} converges toward \eqref{eq:laplace-beltrami} as $t\rightarrow 0$. In particular, this second step is given by the following:
\begin{prop}
[\cite{belkin2005towards}, Proposition 4.4]
Let $\mathcal{M}$ be a $k$-dimensional compact smooth manifold embedded in some Euclidean space $\mathbb{R}^N$, and fix $y\in\mathcal{M}$. Let $f\in\mathcal{C}_\infty(\mathcal{M)}$. Then
\begin{equation}
\frac{1}{t}\frac{1}{(4\pi t)^{k/2}} L^tf(y) \xrightarrow{t\to 0 } \frac{1}{\text{vol}(\mathcal M)}\Delta_{\mathcal M}f(y).
\end{equation}
\label{prop:3}
\end{prop}
